big stoch sim

### 2023-01-19 report/cs_analysis.Rmd
Simulations filtered by faisability of FW (C/S) + test garbage collector

---
title: big sim
author: Alain Danet
output:
  bookdown::pdf_document2
---

```{r}
library(tidyverse)
library(magrittr)
```

```{r}
df_brut <- read_csv(here::here("res", "cs_sim.csv"))
df <- df_brut %>%
  select(where(is.double))
```

```{r}
summary(df)

df %>%
  filter(stab_com <= 1000) %>%
  ggplot(aes(x = as.factor(richness), y = stab_com, color = as.factor(ct))) +
  geom_boxplot()
```

@@

>>>>

---
title: Simulation connectance richness
author: Alain Danet
output:
  bookdown::pdf_document2
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

```{r, results = FALSE}
library(tidyverse)
library(magrittr)
library(cowplot)
library(here)

mytheme <- theme_cowplot(font_size = 8) +
background_grid() +
theme(legend.position = "bottom")

theme_set(mytheme)
```

```{r}
df_brut <- read_csv(here::here("res", "cs_sim.csv"))
df <- df_brut %>%
  select(where(is.double))
summary(df)
```

```{r}
df %>%
  filter(stab_com <= 1000) %>%
  mutate(stab_pop = 1/ avg_cv_sp) %>%
  pivot_longer(
    c(stab_com, stab_pop, sync),
    names_to = "metric",
    values_to = "stab") %>%
  ggplot(aes(x = as.factor(richness), y = stab, color = as.factor(ct))) +
  geom_boxplot() +
  facet_grid(rows = vars(metric), scales = "free_y") +
  labs(
    color = "Connectance",
    x = "Species richness",
    y = "Stability component"
  )
```

@@

- Main results:
  - Stability increases with richness but not connectance (no overall effect)
  - Richness increases stability by increasing maximum and average trophic
    level, but also by decreasing interaction strength and increasing asymetry
    in trophic interaction, and finally by increasing total biomass (I need to control for that).
  - Synchrony decreases with species richness, max and average trophic level but increases with
    average interaction strength and symetry of interaction distributions.
  - Population varibility decreases with species richness, average and maximum
    trophic level, asymetry of interaction strength but it is increased by
    average interaction strength
  - Same effects of food-web structure on both Synchrony and Population variability
    - Surpringly, as in Danet et al. (2021), connectance has little effect on
      temporal stability and its components!

# Covariation

It seems that the effects of food-web structure are mainly richness effects!

```{r}
df %>%
  filter(stab_com <= 1000) %>%
  mutate(stab_pop = 1/ avg_cv_sp) %>%
  pivot_longer(
    c(stab_com, stab_pop, sync),
    names_to = "metric",
    values_to = "stab") %>%
  ggplot(aes(x = avg_max_int, y = stab, color = as.factor(richness))) +
  geom_point() +
  geom_smooth() +
  facet_grid(rows = vars(metric), scales = "free_y") +
  labs(
    color = "Richness",
    x = "Avg interaction strength",
    y = "Stability component"
  )

```

```{r}
df %>%
  filter(stab_com <= 1000) %>%
  mutate(stab_pop = 1/ avg_cv_sp) %>%
  pivot_longer(
    c(stab_com, stab_pop, sync),
    names_to = "metric",
    values_to = "stab") %>%
  ggplot(aes(x = gini_max_int, y = stab, color = as.factor(richness))) +
  geom_point() +
  geom_smooth() +
  facet_grid(rows = vars(metric), scales = "free_y") +
  labs(
    color = "Richness",
    x = "Gini interaction strength",
    y = "Stability component"
  )

```

```{r}
df %>%
  filter(stab_com <= 1000) %>%
  mutate(stab_pop = 1/ avg_cv_sp) %>%
  pivot_longer(
    c(stab_com, stab_pop, sync),
    names_to = "metric",
    values_to = "stab") %>%
  ggplot(aes(x = ct, y = stab, color = as.factor(richness))) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_grid(rows = vars(metric), scales = "free_y") +
  labs(
    color = "Richness",
    x = "Connectance",
    y = "Stability component"
  )
```

```{r}
df %>%
  filter(stab_com <= 1000) %>%
  mutate(stab_pop = 1/ avg_cv_sp) %>%
  pivot_longer(
    c(stab_com, stab_pop, sync),
    names_to = "metric",
    values_to = "stab") %>%
  ggplot(aes(x = w_avg_tlvl, y = stab, color = as.factor(richness))) +
  geom_point() +
  geom_smooth() +
  facet_grid(rows = vars(metric), scales = "free_y") +
  labs(
    color = "Richness",
    x = "Avg trophic level",
    y = "Stability component"
  )
```

### 2023-01-19 report/module_analysis.Rmd
Simulations filtered by faisability of FW (C/S) + test garbage collector

---
title: big stoch sim
author: alain
date: 2022-09-12
format:
  html:
    embed-resources: false
---

```{r}
library(arrow)
library(tidyverse)
library(magrittr)
```

@@

>>>>

---
title: big stoch sim
author: alain
date: 2022-09-12
output:
  bookdown::pdf_document2
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

```{r, results = FALSE}
library(tidyverse)
library(magrittr)
library(cowplot)
library(here)
library(arrow)

mytheme <- theme_cowplot(font_size = 8) +
background_grid() +
theme(legend.position = "bottom")

theme_set(mytheme)
```

@@

# Stochastic natural death

## Competition

```{r}
comp_brut <- open_dataset(here::here("res", "sim_module_competition.arrow"), format = "arrow")
comp <- comp_brut %>%
  collect()
colnames(comp)
```

```{r, eval = FALSE}
unique(comp$env_stoch)
summary(comp$total_biomass)
```

```{r}
comp %>%
  filter(env_stoch == 0.5) %>%
  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
  "values") %>%
  ggplot(aes(x = as.factor(richness), y = values, color = as.factor(alpha_ij))) +
  geom_boxplot() +
  facet_grid(
    rows = vars(stab), cols = vars(rho),
    scales = "free_y") +
  labs(x = "Species richness", y = "Stability component", color = "Interspecific competition")
```

- Main results:
  - Species richness increases stability
  - Interspecific competition does not affect stability expect when
    interspecific competition equals to intraspecific competition (decrease the effect of species richness).
  - Interspecific competition desynchronises primary producers but increases
    varibility
  - The decrease of response diversity decreases the effect of species richness on stability
  - The decrease of response diversity increase synchrony but decrease
    population variability

## Modules

```{r}
mod_brut <- open_dataset(here::here("res", "sim_module_d.arrow"), format = "arrow")
mod <- mod_brut %>%
  collect() %>%
  select(where(is.numeric) | starts_with("module"))
colnames(mod)
```

```{r, eval = FALSE}
unique(mod$env_stoch)
summary(as_tibble(mod))
```

```{r}
mod %>%
  filter(rho == 0, env_stoch == .5) %>%
  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
  "values") %>%
  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
  geom_boxplot() +
  facet_grid(rows = vars(stab), scales = "free_y")

```

```{r}
mod %>%
  filter(rho == 0.5, env_stoch == .5) %>%
  pivot_longer(c(stab_com, sync, avg_cv_sp), names_to = "stab", values_to =
  "values") %>%
  ggplot(aes(x = module_name, y = values, color = as.factor(alpha_ij))) +
  geom_boxplot() +
  facet_grid(rows = vars(stab), scales = "free_y")

```
